Code Overflow: \\ An empirical study of online code reuse

### 2016-08-23 latex/stackoverflow.tex
Added individual results

\begin{tabular}{l|r|r|c|p{5cm}|p{3cm}}

@@

	Projects & Old version & New versions & Latest change & License & Notes \\

@@

	ArgoUML & 0.34 & 0.35.1 & 15/01/2014 & Eclipse Public License v.1.0 \\
	Compiere & 330 & -- & 01/06/2010 &  GNU General Public License v.2.0 & No longer OSS \\
	FitLibrary & 20100806 & 20111026 & 12/07/2014 & GNU General Public License v.2.0 \\
	JGroups & 2.10.0.GA & 3.6.10 & 27/06/2016  & Apache License, v.2.0 \\
	Vuze & 4812 & 5721-20 & 12/05/2016 & GNU General Public License v.2.0 &  \\
	antlr4 & 4.0 & 4.2.1 & 15/01/2014 & BSD License \\
	aoisrc & 281 & 302 & 12/01/2015 &  GNU General Public License v.2.0 \\
	apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & Apache License, v.2.0 \\
	aspectj & 1.6.9 & 1.8.9 & 14/03/2015 & Eclipse Public License 1.0 \\
	axion & 1.0-M2 & -- & 08/03/2013 & Proprietary (BSD/Apache-style) \\
	batik & 1.7 & 1.8 & 16/03/2015 & Apache License, v.2.0 \\
	c-jdbc & 2.0.2 & -- & 16/09/2005 & GNU Lesser General Public License, v.2.1 \\
	castor & 1.3.1 & 1.4.2 & 20/06/2016 & Apache License, v.2.0 \\
	cayenne & 3.0.1 & 4.0.M4 &  27/07/2016 & Apache License, v.2.0 \\
	checkstyle & 5.1 & 7.2  & 04/08/2016 & GNU Lesser General Public License, v.2.1 \& Apache License, v.2.0 & \textit{Cli, Logging and Beanutils} packages are from the Apache Commons project. \\
	cobertura & 1.9.4.1 & 2.1.2 & 01/06/2015 & GNU General Public License v.2.0  \\
	colt & 1.2.0 & -- & 09/09/2014 &  Proprietary (CERN) \\
	columba & 1.4 & -- & 20/04/2007 & Mozilla Public License 1.1  \\
	commons-collections & 3.2.1 & 4.1 & 25/11/2015 & Apache License, v.2.0 \\
	db-derby & 10.6.1.0 & 10.12.1.1 & 13/09/2015 & Apache License, v.2.0 \\
	displaytag & 1.2 & 2.0 & 17/08/2014 & MIT License \\
	drawswf & 1.2.9 & -- & 02/04/2013 & GNU General Public License v.2.0 \\
	drjava & 20100913-r5387 & 20140826-r5761 & 26/08/2014 & BSD License \\
	eXoPortal & ??? & 4.4 & 24/06/2016 & GNU Lesser General Public License v.3.0 \& proprietary \\
	emma & 2.0.5312 & 2.0.5312 & 09/05/2013  & Common Public License 1.0 \\
	findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & GNU Lesser General Public License, v.2.0 \\
	fit-java & 1.1 & -- & 04/06/2013 & GNU General Public License v.2.0 \\
	freecol & 0.10.7 & 0.11.6 & 04/08/2016 & GNU General Public License v.2.0 &  \\
	freecs & 1.3.20100406 & -- & 22/04/2013 & GNU General Public License v.3.0 &   \\
	freemind & 0.9.0 & 1.0.0 & 26/06/2016 & GNU General Public License v.2.0+ &  \\
	galleon & 2.3.0 & 2.5.6 & 29/04/2013 & GNU General Public License v.2.0 \\
	ganttproject & 2.0.9 & 2.8.1 & 05/08/2016 & GNU General Public License v.3.0 &  \\
	geotools & 2.7-M3 & 16 & 02/08/2016 & GNU Lesser General Public License, v.2.0 \\
	hadoop & 1.0.0 & 2.6.4 & 11/02/2016 & Apache License, v.2.0 \\
	heritrix & 1.14.4 & -- & 05/06/2013 & GNU Lesser General Public License, v.2.1 \\
	hibernate & 4.2.2 & 5.2.2 & 04/08/2016 & GNU Lesser General Public License, v.2.1+ \\
	hsqldb & 2.0.0 & 2.3.4 & 16/05/2016 & BSD License \\
	htmlunit & 2.8 & 2.24 & 27/07/2016 & Apache License, v.2.0 \\
	iReport & 3.7.5 & -- & 28/05/2014 & Affero GNU Public License, v.3.0 \\
	iText & 5.0.3 & 7.0.0 & 02/05/2016 & Affero GNU Public License, v.3.0 \\
	informa & 0.7.0-alpha2 & -- & 07/11/2008 & GNU Lesser General Public License, v.2.1 \& Apache Software License, v.1.1 \\
	ivatagroupware & 0.11.3 & -- & 27/02/2013  & GNU General Public License v.2.0 \\
	jFin DateMath & R1\_0\_1 & -- & 25/04/2013  & GNU General Public License v.2.0 \\
	jOggPlayer & 114s & -- &  15/04/2013   & GNU General Public License v.2.0 \\
	jag & 6.1 & 6.2 & 08/04/2013   & GNU General Public License v.2.0 \& BSD License & BSD License is for libraries they use. \\
	james & 2.2.0 & 2.3.2.1 & 14/08/2015 & Apache License, v.2.0 \\
	jasml & 0.10 & -- & 08/03/2013 & Apache Software License \\
	jasperreports & 3.7.4 & 6.3.1 & 20/06/2016 & GNU Lesser General Public License, v.3.0 &  \\
	javacc & 5.0.0 & 7.0.0 & 07/07/2016 & Proprietary (Sun) \\
	jboss (Wildfly) & 5.1.0.GA & 10.0.0 & 29/01/2016 & GNU Lesser General Public License, v.2.1 & It is renamed to Wildfly. \\
	jchempaint & 3.0.1 & 3.1.3 & 18/04/2016 & GNU Lesser General Public License, v.2.1+ &  \\
	jedit & 4.3.2 & 5.3.0 & 20/10/2015  & GNU General Public License v.2.0 &  \\
	jena & 2.6.3 & 3.1.0 & 10/05/2016 & Apache License, v.2.0 \\
	jext & 5.0 & -- & 18/08/2004   & GNU General Public License v.2.0 &  \\
	jfreechart & 1.0.13 & 1.2.0-ea1 & 08/05/2016  & GNU Lesser General Public License, v.2.0 &   \\
	jgraph & 5.13.0.0 & 3.5.1.5 & 20/07/2016 & Proprietary (mxGraph License) \\
	jgraphpad & 5.10.0.2 & -- & 10/11/2006 & GNU General Public License  \& GNU Lesser General Public License (derivatives) \\
	jgrapht & 0.8.1 & 0.9.2 & 03/04/2016 & GNU Lesser General Public License, v.2.1 \& Eclipse Public License, v.1.0 \\
	jmoney & 0.4.4 & -- & 17/04/2016 & GNU General Public License v.2.0 &  \\
	jparse & 0.96 & -- & 29/07/2004 & GNU Lesser General Public License, v.2.1 \\
	jpf & 1.5.1 & ??? & 13/01/2012 & Apache License, v.2.0 \\
	junit & 4.11 & 4.12 & 04/12/2014 & Eclipse Public License, v.1.0 \\
	shiftone-jrat & 0.6 & 1-beta-1 & 25/04/2013 & GNU Lesser General Public License, v.2.0 &  \\

@@

\end{tabular} 

>>>>

	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|r|c|c|p{5cm}|p{3cm}}

@@

	Projects & Old version & New versions & Latest change & Repo. & License & Notes \\

@@

	ArgoUML & 0.34 & 0.35.1 & 15/01/2014 	& & Eclipse Public License v.1.0 \\
	Compiere & 330 & -- & 01/06/2010 		& git & GNU General Public License v.2.0 & No longer OSS \\
	FitLibrary & 20100806 & 20111026 & 12/07/2014 & & GNU General Public License v.2.0 \\
	JGroups & 2.10.0.GA & 3.6.10 & 27/06/2016 & & Apache License, v.2.0 \\
	Vuze & 4812 & 5721-20 & 12/05/2016 & & GNU General Public License v.2.0 &  \\
	antlr4 & 4.0 & 4.2.1 & 15/01/2014 & & BSD License \\
	aoisrc & 281 & 302 & 12/01/2015 & & GNU General Public License v.2.0 \\
	apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & git & Apache License, v.2.0 \\
	aspectj & 1.6.9 & 1.8.9 & 14/03/2015 & & Eclipse Public License 1.0 \\
	axion & 1.0-M2 & -- & 08/03/2013 & & Proprietary (BSD/Apache-style) \\
	batik & 1.7 & 1.8 & 16/03/2015 & & Apache License, v.2.0 \\
	c-jdbc & 2.0.2 & -- & 16/09/2005 & & GNU Lesser General Public License, v.2.1 \\
	castor & 1.3.1 & 1.4.2 & 20/06/2016 & git & Apache License, v.2.0 \\
	cayenne & 3.0.1 & 4.0.M4 &  27/07/2016 & git & Apache License, v.2.0 \\
	checkstyle & 5.1 & 7.2  & 04/08/2016 & git & GNU Lesser General Public License, v.2.1 \& Apache License, v.2.0 & \textit{Cli, Logging and Beanutils} packages are from the Apache Commons project. \\
	cobertura & 1.9.4.1 & 2.1.2 & 01/06/2015 & git & GNU General Public License v.2.0  \\
	colt & 1.2.0 & -- & 09/09/2014 & & Proprietary (CERN) \\
	columba & 1.4 & -- & 20/04/2007 & & Mozilla Public License 1.1  \\
	commons-collections & 3.2.1 & 4.1 & 25/11/2015 & & Apache License, v.2.0 \\
	db-derby & 10.6.1.0 & 10.12.1.1 & 13/09/2015 & & Apache License, v.2.0 \\
	displaytag & 1.2 & 2.0 & 17/08/2014 & svn & MIT License \\
	drawswf & 1.2.9 & -- & 02/04/2013 & & GNU General Public License v.2.0 \\
	drjava & 20100913-r5387 & 20140826-r5761 & 26/08/2014 & & BSD License \\
	eXoPortal & ??? & 4.4 & 24/06/2016 & git & GNU Lesser General Public License v.3.0 \& proprietary \\
	emma & 2.0.5312 & 2.0.5312 & 09/05/2013  & & Common Public License 1.0 \\
	findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & & GNU Lesser General Public License, v.2.0 \\
	fit-java & 1.1 & -- & 04/06/2013 & & GNU General Public License v.2.0 \\
	freecol & 0.10.7 & 0.11.6 & 04/08/2016 & git & GNU General Public License v.2.0 &  \\
	freecs & 1.3.20100406 & -- & 22/04/2013 & & GNU General Public License v.3.0 &   \\
	freemind & 0.9.0 & 1.0.0 & 26/06/2016 & & GNU General Public License v.2.0+ &  \\
	galleon & 2.3.0 & 2.5.6 & 29/04/2013 & & GNU General Public License v.2.0 \\
	ganttproject & 2.0.9 & 2.8.1 & 05/08/2016 & & GNU General Public License v.3.0 &  \\
	geotools & 2.7-M3 & 16 & 02/08/2016 & git & GNU Lesser General Public License, v.2.0 \\
	hadoop & 1.0.0 & 2.6.4 & 11/02/2016 & & Apache License, v.2.0 \\
	heritrix & 1.14.4 & -- & 05/06/2013 & & GNU Lesser General Public License, v.2.1 \\
	hibernate & 4.2.2 & 5.2.2 & 04/08/2016 & git & GNU Lesser General Public License, v.2.1+ \\
	hsqldb & 2.0.0 & 2.3.4 & 16/05/2016 & svn & BSD License \\
	htmlunit & 2.8 & 2.24 & 27/07/2016 & svn & Apache License, v.2.0 \\
	iReport & 3.7.5 & -- & 28/05/2014 & & Affero GNU Public License, v.3.0 \\
	iText & 5.0.3 & 7.0.0 & 02/05/2016 & & Affero GNU Public License, v.3.0 \\
	informa & 0.7.0-alpha2 & -- & 07/11/2008 & & GNU Lesser General Public License, v.2.1 \& Apache Software License, v.1.1 \\
	ivatagroupware & 0.11.3 & -- & 27/02/2013 & & GNU General Public License v.2.0 \\
	jFin DateMath & R1\_0\_1 & -- & 25/04/2013 & & GNU General Public License v.2.0 \\
	jOggPlayer & 114s & -- &  15/04/2013 &  & GNU General Public License v.2.0 \\
	jag & 6.1 & 6.2 & 08/04/2013  & & GNU General Public License v.2.0 \& BSD License & BSD License is for libraries. \\
	james & 2.2.0 & 2.3.2.1 & 14/08/2015 & & Apache License, v.2.0 \\
	jasml & 0.10 & -- & 08/03/2013 & & Apache Software License \\
	jasperreports & 3.7.4 & 6.3.1 & 20/06/2016 & git & GNU Lesser General Public License, v.3.0 &  \\
	javacc & 5.0.0 & 7.0.0 & 07/07/2016 & svn & Proprietary (Sun) \\
	jboss (Wildfly) & 5.1.0.GA & 10.0.0 & 29/01/2016 & & GNU Lesser General Public License, v.2.1 & Renamed to Wildfly. \\
	jchempaint & 3.0.1 & 3.1.3 & 18/04/2016 & git & GNU Lesser General Public License, v.2.1+ &  \\
	jedit & 4.3.2 & 5.3.0 & 20/10/2015 & & GNU General Public License v.2.0 &  \\
	jena & 2.6.3 & 3.1.0 & 10/05/2016 & & Apache License, v.2.0 \\
	jext & 5.0 & -- & 18/08/2004 &  & GNU General Public License v.2.0 &  \\
	jfreechart & 1.0.13 & 1.2.0-ea1 & 08/05/2016 & svn & GNU Lesser General Public License, v.2.0 &   \\
	jgraph & 5.13.0.0 & 3.5.1.5 & 20/07/2016 & git & Proprietary (mxGraph License) \\
	jgraphpad & 5.10.0.2 & -- & 10/11/2006 & & GNU General Public License  \& GNU Lesser General Public License (derivatives) \\
	jgrapht & 0.8.1 & 0.9.2 & 03/04/2016 & & GNU Lesser General Public License, v.2.1 \& Eclipse Public License, v.1.0 \\
	jmoney & 0.4.4 & -- & 17/04/2016 & & GNU General Public License v.2.0 &  \\
	jparse & 0.96 & -- & 29/07/2004 & & GNU Lesser General Public License, v.2.1 \\
	jpf & 1.5.1 & ??? & 13/01/2012 & & Apache License, v.2.0 \\
	junit & 4.11 & 4.12 & 04/12/2014 & & Eclipse Public License, v.1.0 \\
	shiftone-jrat & 0.6 & 1-beta-1 & 25/04/2013 & svn & GNU Lesser General Public License, v.2.0 &  \\

@@

\end{tabular} %
}
